<!--- Describe raw data here (just the starting material) --->

Before beginning the analysis, there are several datasets that must be downloaded. The following sections provide detailed instructions for downloading all required datasets.

## Coding sequence coordinates

Coding sequence (CDS) coordinates can be downloaded from the UCSC genome browser with the following command.

```{r echo = TRUE, eval = FALSE}
data_import$CDS(save_as = 'data/CDS/Hsapiens-UCSC-hg38.csv')
data_import$CDS_contiguous_intervals(
  given   = 'data/CDS/Hsapiens-UCSC-hg38.csv', 
  save_as = 'data/CDS/Hsapiens-UCSC-hg38-contiguous-intervals.csv'
)
```

## Cosmic

To download the [Catalogue of Somatic Mutations in Cancer](https://cancer.sanger.ac.uk/cosmic/download) [@ForbesCOSMICsomaticcancer2017], first [register with a valid email address](https://cancer.sanger.ac.uk/cosmic/register), then download the `CosmicMutantExport.tsv.gz` dataset into the `data/COSMIC` directory using the following commands:

```shell
# In Terminal
cd data/COSMIC
sftp "your@email.com"@sftp-cancer.sanger.ac.uk         # Enter password when prompted
get /files/grch38/cosmic/v83/CosmicMutantExport.tsv.gz
get /files/grch38/cosmic/v83/VCF/CosmicCodingMuts.vcf.gz
```

After downloading the main Cosmic dataset, we will generate three processed versions of this dataset using the following commands. 

```{r echo = TRUE, eval = FALSE}
data_import$COSMIC_vcf_to_csv(
  given   = 'data/COSMIC/CosmicCodingMuts.vcf.gz',
  save_as = 'data/COSMIC/Cosmic-Coding.csv'
)
data_import$COSMIC_nonsense(
  given   = 'data/COSMIC/Cosmic-Coding.csv',
  save_as = 'data/COSMIC/Cosmic-Nonsense.csv'
)
```

## ClinVar

[Clinical Variants](https://www.ncbi.nlm.nih.gov/clinvar/) can be downloaded using the following commands:

```shell
# In Terminal
# On macOS `wget` can be installed via homebrew `brew install wget`
cd data/ClinVar
wget ftp://ftp.ncbi.nlm.nih.gov/pub/clinvar/tab_delimited/variant_summary.txt.gz
wget ftp://ftp.ncbi.nlm.nih.gov/pub/clinvar/tab_delimited/allele_gene.txt.gz
wget ftp://ftp.ncbi.nlm.nih.gov/pub/clinvar/tab_delimited/README
wget ftp://ftp.ncbi.nlm.nih.gov/pub/clinvar/README_VCF.txt
wget ftp://ftp.ncbi.nlm.nih.gov/pub/clinvar/vcf_GRCh38/clinvar.vcf.gz
```

```{r echo = TRUE, eval = FALSE}
data_import$ClinVar_vcf_to_csv(
  given   = 'data/ClinVar/clinvar.vcf.gz',
  save_as = 'data/ClinVar/ClinVar.csv'
)
data_import$ClinVar_nonsense(
  given   = 'data/ClinVar/ClinVar.csv',
  save_as = 'data/ClinVar/ClinVar-Nonsense.csv'
)
```

## Coriell

Go to [Coriell](https://www.coriell.org/0/Sections/BrowseCatalog/Genes.aspx?PgId=5) and enter `*.*` into the search bar. Then click on `Export to Excel` and, when prompted, check the boxes for `ID`, `Description`, `Gene` and `Mutations`. Then click `Export All Samples in Grid`. Move this file to the `data/Coriell` directory of this project and rename the file to `Catalog-Export.csv`.
